Automated Topic Naming

### 2012-01-19 ese/ese.tex
migod changes in section 4/5

%\noindent \textbf{Generating labels automatically} ---

@@

%\DONE{this discussion is about which DB? where do the numbers come from?}
For \textsf{exp1} the labels with the most topics
were
%XXX Neil                    V changed from 748 is that right?
\emph{correctness} (182/305/640, which represent MySQL, MaxDB and PostgreSQL topic counts, respectively) and \emph{testability} (121/238/625). 
We did not see many results for \emph{usability} (4/0/138) or
\emph{accuracy} (3/0/27), which were infrequently matched. Note the significantly higher result for \emph{usability} in PostgreSQL -- this suggests a difference in how this project is discussing usability, at least with respect to our analysis.
We also looked for correlations between our labels: excluding double
matches (self-correlation), our highest co-occurring terms were
\emph{verifiability} or \emph{correctness}
with \emph{traceability}, and \emph{testability} with \emph{correctness}.% (76 and 62 matches, respectively).
% See the following sections for our error analysis.

@@

For \textsf{exp3}, we generally labelled more topics. 
As we mentioned, the word-lists are broad, so there are likely to be false-positives (discussed below). 
The most frequent label across all projects (for this wordlist, and unlike \textsf{exp1}) was \emph{usability}, and the
least frequent label was \emph{maintainability}. This implies that our signifiers for usability in this experiment were fairly broad.
Common co-occurrences were \emph{reliability} with \emph{usability}, \emph{efficiency} with \emph{reliability}, and \emph{efficiency} with \emph{usability}.
%(200, 190, and 150 topics in common, respectively).

@@

To assess the performance of the supervised learners, we did a 10-fold cross-validation~\cite{Kohavi1995}, a common technique for evaluating machine
learners. 
The original data is partitioned randomly into ten sub-samples. Each sample is used to test against a training set composed of the nine other samples.
%One subsample is used as a training set and evaluated on the other nine sub-samples. 
%This is repeated nine more times, with each subsample used once as the training set. 
We have reported these results below.% in Section \ref{sec:suplabelling}.

\subsubsection{Analysis of the Supervised Labelling}
% \label{sec:suplabelling}
Because our data-set was of word counts we expected Bayesian techniques, often used in spam filtering, to perform well. 
We tried other learners that WEKA~\cite{weka09} provides: rule learners, decision tree learners, vector space learners, and support vector machines.  
Figure \ref{fig:best-learn-per-tag} shows the performance of the best
performing learner per label: 
% We considered the best learner for a label to be 
the learner that had the highest ROC value for that label. 
The best learner is important because one uses a single learner per
label. When applying our technique, for each NFR one should select the
best performing learner possible. Given the tractability of these techniques, a tool which applied all learners and presented the best result should be feasible. 
%Figure \ref{fig:best-learn-per-tag} uses the ZeroR learner as a baseline, a common practice in machine learning,
%as ZeroR naively chooses the largest category all of the time. 
%ZeroR occasionally outperforms other learners; for labels which are not as common, this is to be expected because any miscategorization will hurt accuracy. 
%This is why we use ROC values, instead of accuracy, as they can better represent performance on labels which are not applicable to the majority of samples.

@@

For all projects Bayesian techniques did the best out of a wide variety of machine learners tested, due to the large number of features they can handle.
Our best learners, Discriminative Multinomial Naive Bayes, Naive Bayes
and Multinomial Naive Bayes  are all based on Bayes' theorem and all
assume, naively, that the features supplied are independent. 
%The features we used are word counts per message. 
One beneficial aspect of this result is that it suggests we can have
very fast training and classifying  since training on or classifying one
instance with Naive Bayes can be calculated in $O(N)$
for $N$ features.
%http://nlp.stanford.edu/IR-book/html/htmledition/naive-bayes-text-classification-1.html

@@

As noted in Section \ref{sec:wordlist}, each topic in our data-set can be composed of zero or more NFRs. 
For example, a commit message might address \textit{reliability} in the context of \textit{efficiency}, or make a \textit{maintainability} improvement
in the source code that related to \textit{usability}. 
However, traditional machine learning techniques, such as Naive Bayes, can only map topics to a single class. 
The Mulan~\cite{mulan} library encapsulates several different multi-label machine learners which can label elements with multiple labels.
Mulan also includes methods for determining the performance of these learners.
% TOO DETAILED The problem framed in the learners above has changed; instead of looking at the precision and recall of applying one label, we rank
% multiple labels at once. We must check if the full subset of labels was applied, and then how much of that subset was applied.

@@

\section{Understanding Software Maintenance Activities} 
\label{sec:analysis}
As we mentioned in the introduction, a key issue in software maintenance is understanding \emph{why} a system has evolved the way it has~\cite{aranda09icse}. 
In this section we demonstrate the value of labelled topic extraction
in addressing this issue. 
% more why
Labelled topics address \emph{why}  because they show reasons why changes
occurred rather than \emph{how}. 
The \emph{how} of a change is the change itself, the purpose or
\emph{why} is what we are after.
We investigate the history of the three large-scale database systems that we studied. 
We use our technique to show the topic of development efforts over time in each project.
%We evaluated two research questions using the ground truth data that we annotated by hand:
We motivated our investigation with three research questions:
\begin{enumerate}
\item \emph{Do NFR frequencies change over time?} If a particular NFR
  was of more interest at one point in the life-cycle than another,
  this suggests that development activity shifted focus. For example,
  if a developer expected to see a recent focus on \emph{reliability},
  but instead \emph{usability} dominated, they might re-prioritize
  upcoming work items.

>>>>

@@

%\DONE{this discussion is about which DB? where do the numbers come from?}
For \textsf{exp1} the labels with the most topics
were
%XXX Neil                    V changed from 748 is that right?
\emph{correctness} (182/305/640, which represent MySQL, MaxDB and PostgreSQL topic counts, respectively) and \emph{testability} (121/238/625). 
We did not see many results for \emph{usability} (4/0/138) or
\emph{accuracy} (3/0/27), which were infrequently matched. Note the significantly higher result for \emph{usability} in PostgreSQL---this suggests a difference in how project developers are discussing usability, at least with respect to our analysis.
We also looked for correlations between our labels: excluding double
matches (self-correlation), our highest co-occurring terms were
\emph{verifiability} or \emph{correctness}
with \emph{traceability}, and \emph{testability} with \emph{correctness}.% (76 and 62 matches, respectively).
% See the following sections for our error analysis.

@@

For \textsf{exp3}, we generally labelled more topics. 
As mentioned above, the word-lists are broad, so there are likely to be false-positives (discussed below). 
The most frequent label across all projects (for this wordlist, and unlike \textsf{exp1}) was \emph{usability}, and the
least frequent label was \emph{maintainability}. This implies that our signifiers for usability in this experiment were fairly broad.
Common co-occurrences were \emph{reliability} with \emph{usability}, \emph{efficiency} with \emph{reliability}, and \emph{efficiency} with \emph{usability}.
%(200, 190, and 150 topics in common, respectively).

@@

To assess the performance of the supervised learners, we did a 10-fold cross-validation~\cite{Kohavi1995}, a common technique for evaluating machine
learners, where the original data is partitioned randomly into ten sub-samples, and each sample is used to test against a training set composed of the nine other samples.
%One subsample is used as a training set and evaluated on the other nine sub-samples. 
%This is repeated nine more times, with each subsample used once as the training set. 
We discuss these results below.% in Section \ref{sec:suplabelling}.

\subsubsection{Analysis of the Supervised Labelling}
% \label{sec:suplabelling}
Because our data-set consisted of word counts we expected Bayesian techniques to perform well. Bayesian techniques are often used in spam filtering, which is similarly interested in word distributions. 
We tried other learners that WEKA~\cite{weka09} provides, including rule learners, decision tree learners, vector space learners, and support vector machines.  
Figure \ref{fig:best-learn-per-tag} shows the performance of the best
performing learner per label: 
% We considered the best learner for a label to be 
the learner that had the highest ROC value for that label. 
The best learner is important because one uses a single learner per
label. When applying our technique, for each NFR one should select the
best performing learner possible. Given the tractability of these techniques, a tool which applied all learners and presented the best result should be feasible. 
%Figure \ref{fig:best-learn-per-tag} uses the ZeroR learner as a baseline, a common practice in machine learning,
%as ZeroR naively chooses the largest category all of the time. 
%ZeroR occasionally outperforms other learners; for labels which are not as common, this is to be expected because any miscategorization will hurt accuracy. 
%This is why we use ROC values, instead of accuracy, as they can better represent performance on labels which are not applicable to the majority of samples.

@@

Although we used a variety of machine learners, we found that Bayesian techniques performed the best on all projects. We believe this is due to the large number of features they can handle.
Our best-performing learners---Discriminative Multinomial Naive Bayes, Naive Bayes
and Multinomial Naive Bayes---are all based on Bayes' theorem and all make the naive assumption
that the features supplied are independent. 
%The features we used are word counts per message. 
One beneficial aspect of this result is that it suggests we can have
very fast training and classifying  since training on or classifying one
instance with Naive Bayes can be calculated in $O(N)$
for $N$ features.
%http://nlp.stanford.edu/IR-book/html/htmledition/naive-bayes-text-classification-1.html

@@

As noted in Section \ref{sec:wordlist}, each topic in our data-set can be composed of zero or more NFRs. 
For example, a commit message might address \textit{reliability} in the context of \textit{efficiency}, or make a \textit{maintainability} improvement
in the source code that relates to \textit{usability}. 
However, traditional machine learning techniques, such as Naive Bayes, can map topics to only a single class. 
The Mulan~\cite{mulan} library encapsulates several different multi-label machine learners which can label elements with multiple labels.
Mulan also includes methods for determining the performance of these learners.
% TOO DETAILED The problem framed in the learners above has changed; instead of looking at the precision and recall of applying one label, we rank
% multiple labels at once. We must check if the full subset of labels was applied, and then how much of that subset was applied.

@@

\section{Understanding Software Maintenance Activities} 
\label{sec:analysis}
As we mentioned in the introduction, a key issue in software maintenance is understanding \emph{why} a system has evolved the way it has~\cite{aranda09icse}. 
In this section we demonstrate the value of labelled topic extraction
in addressing this issue. 
% more why
Labelled topics address \emph{why} questions by associating a commit with the underlying software qualities which motivated that change.
The \emph{how} of a change is the change itself, the software quality behind it, the
\emph{why} is what we are after.
We investigate the history of the three large-scale database systems that we studied. 
We use our technique to show the topic of development efforts over time in each project.
%We evaluated two research questions using the ground truth data that we annotated by hand:
We motivated our investigation with three research questions:
\renewcommand{\labelenumi}{\textbf{RQ\arabic{enumi}. }}
\begin{enumerate}
\item \emph{Do NFR frequencies change over time?} If a particular NFR
  was of more interest at one point in the life-cycle than another,
  this suggests that development activity shifted focus. For example,
  if a developer expected to see a recent focus on \emph{reliability},
  but instead \emph{usability} dominated, they might re-prioritize
  upcoming work items.
